Three Algorithms for Merging Hierarchical Navigable Small World Graphs

### 2025-05-21 paper/main.tex
Add link to repo into the paper

\[
\text{recall@}k = \frac{|P_k(q) \cap A_k(q)|}{k}
\]

In our experiment as recall@5 we report an averaged value over all sequences of searches.

>>>>

\[
\text{recall@}k = \frac{|P_k(q) \cap A_k(q)|}{k}
\]
In our experiment as recall@5 we report an averaged value over all sequences of searches.

All source codes of our implementation can be found in a public GitHub repository \footnote{\url{https://github.com/aponom84/merging-navigable-graphs}}.
